---
title: "Intentional Binding Report - Multiple Subjects"
author: "Transpsychlab (www.transpsychlab.org)"
output:
html_document:
theme: united
---

This is a multiple-subject report for Intentional Binding paradigm [Brain 2010].

**Data:** `r flname`

**Total Trails with missing data**: `r length(dataset$CleanTrial[dataset$CleanTrial == FALSE]) `

###Mixed design ANOVA with Status as between-subjects factor and experimental conditions as within-subjects factor

**Mixed design ANOVA - Effect of Status and Tone presence**
```{r, echo = FALSE, comment="  "}
aov_status_tonepre <- aov(JudgeErrorOutBL ~ Status*TonePresence + Error(Name/TonePresence), data=dataSE1)
summary(aov_status_tonepre)
```

```{r, echo = FALSE, comment="  ",fig.width =6, fig.height=6,fig.align ='center', warning=FALSE}
figdataSE1 <- summarySE(dataset, measurevar="JudgeErrorOutBL", groupvars=c("Status","TonePresence"), na.rm = TRUE)
ggplot(data=figdataSE1, aes(x=TonePresence, y=JudgeErrorOutBL, fill=Status)) +  geom_bar(position=position_dodge(), stat="identity") + geom_errorbar(aes(ymin=JudgeErrorOutBL-se, ymax=JudgeErrorOutBL+se), width=.2, position=position_dodge(.9)) + geom_point(pch=21, col="black", cex = 4, aes(colour = Status),position=position_dodge(.9)) + geom_hline(yintercept=0) + ggtitle("Effect of tone presence in patients and controls\nBar plot showing means & standard errors") + xlab("Presence of Tone") +  ylab("Mean Shift from Baseline [ms]") + scale_fill_brewer(palette="Set1", name="Status", breaks=c("Cntrl", "SCZ"), labels=c("Healthy Controls", "Schizophrenia Patients")) +  theme(axis.title = element_text(face="bold", size=12), axis.text  = element_text(face="bold", size=10), axis.ticks = element_blank())
```


**Mixed design ANOVA - Effect of Status and Tone probability [all 3 blocks - 0%, 50%, 75%]**
```{r, echo = FALSE, comment="  "}
aov_status_toneprb <- aov(JudgeErrorOutBL ~ Status*Block + Error(Name/Block), data=dataSE2)
summary(aov_status_toneprb)
```

**Mixed design ANOVA - Effect of Status and Tone probability [2 blocks - 50%, 75%]**
```{r, echo = FALSE, comment="  "}
aov_status_toneprb_5075 <- aov(JudgeErrorOutBL ~ Status*Block + Error(Name/Block), data = subset(dataSE2, Block != "Tone0Trials"))
summary(aov_status_toneprb_5075)
```

```{r, echo = FALSE, comment="  ",fig.width =8, fig.height=6,fig.align ='center', warning=FALSE}
figdataSE2 <- summarySE(dataset, measurevar="JudgeErrorOutBL", groupvars=c("Status","Block"), na.rm = TRUE)
ggplot(data=figdataSE2, aes(x=Block, y=JudgeErrorOutBL, fill=Status)) +  geom_bar(position=position_dodge(), stat="identity") + geom_errorbar(aes(ymin=JudgeErrorOutBL-se, ymax=JudgeErrorOutBL+se), width=.2, position=position_dodge(.9)) + geom_point(pch=21, col="black", cex = 4, aes(colour = Status),position=position_dodge(.9)) + geom_hline(yintercept=0) + ggtitle("Effect of tone probability in patients and controls\nBar plot showing means & standard errors") + xlab("Experimental Condition - Probability of Tone") +  ylab("Mean Shift from Baseline [ms]") + scale_fill_brewer(palette="Set1", name="Status", breaks=c("Cntrl", "SCZ"), labels=c("Healthy Controls", "Schizophrenia Patients")) + scale_x_discrete(breaks=c("Tone0Trials", "Tone50Trials", "Tone75Trials"),labels=c("0%", "50%", "75%")) + theme(axis.title = element_text(face="bold", size=12), axis.text  = element_text(face="bold", size=10), axis.ticks = element_blank())
```

**Mixed design ANOVA - Effect of Status and Tone probability in 'with tone' trials**
```{r, echo = FALSE, comment="  "}
aov_status_toneprb_wtone <- aov(JudgeErrorOutBL ~ Status*Block + Error(Name/Block), data = subset(dataSE3, TonePresence == TRUE))
summary(aov_status_toneprb_wtone)
```

**Mixed design ANOVA - Effect of Status and Tone probability in 'without tone' trials**
```{r, echo = FALSE, comment="  "}
aov_status_toneprb_wotone <- aov(JudgeErrorOutBL ~ Status*Block + Error(Name/Block), data = subset(dataSE3, TonePresence == FALSE))
summary(aov_status_toneprb_wotone)
```

**Mixed design ANOVA - Effect of Status and Tone probability [50% vs 75%] in 'without tone' trials**
```{r, echo = FALSE, comment="  "}
aov_status_toneprb_wotone_5075 <- aov(JudgeErrorOutBL ~ Status*Block + Error(Name/Block), data = subset(dataSE3, TonePresence == FALSE & Block != "Tone0Trials"))
summary(aov_status_toneprb_wotone_5075)
```

```{r, echo = FALSE, comment="  ",fig.width =8, fig.height=8,fig.align ='center', warning=FALSE}
figdataSE3 <- summarySE(dataset, measurevar="JudgeErrorOutBL", groupvars=c("Status","Block","TonePresence"), na.rm = TRUE)
TF_labeller <- function(var, value){
  value <- as.character(value)
  if (var=="TonePresence") { 
    value[value==TRUE] <- "With Tone"
    value[value==FALSE]   <- "Without Tone"
  }
  return(value)
}
ggplot(data = figdataSE3, aes(x=Block, y=JudgeErrorOutBL, fill=Status)) +  geom_bar(position=position_dodge(), stat="identity") + geom_errorbar(aes(ymin=JudgeErrorOutBL-se, ymax=JudgeErrorOutBL+se), width=.2, position=position_dodge(.9)) + geom_point(pch=21, col="black", cex = 4, aes(colour = Status),position=position_dodge(.9)) + geom_hline(yintercept=0) + ggtitle("Effect of tone probability in 'with tone' and 'without tone'\ntrials in patients and controls\nBar plot showing means & standard errors") + xlab("Experimental Condition - Probability of Tone") +  ylab("Mean Shift from Baseline [ms]") + scale_fill_brewer(palette="Set1", name="Status", breaks=c("Cntrl", "SCZ"), labels=c("Healthy Controls", "Schizophrenia Patients")) + scale_x_discrete(breaks=c("Tone0Trials", "Tone50Trials", "Tone75Trials"),labels=c("0%", "50%", "75%")) + theme(axis.title = element_text(face="bold", size=12), axis.text  = element_text(face="bold", size=10), axis.ticks = element_blank()) + facet_grid(TonePresence ~ .,labeller=TF_labeller)
```


###Identifying outliers - Subjects/Block/Tone

####Outliers based on mean of baseline corrected judgement erorrs
```{r, echo = FALSE, comment="  ",fig.width =8, fig.height=6,fig.align ='center', warning=FALSE, fig.cap='Box plot'}
CS_labeller <- function(var, value){
  value <- as.character(value)
  if (var=="Status") { 
    value[value=="Cntrl"] <- "Healthy Controls"
    value[value=="SCZ"]   <- "Schizophrenia Patients"
  }
  return(value)
}
  
ggplot(data=subset(dataSE3, Block != "Tone0Trials"), aes(x=TonePresence, y=JudgeErrorOutBL, fill=Block)) + stat_boxplot(geom ='errorbar')+ geom_boxplot(outlier.size = 0) + ggtitle("All schizophrenia patients and healthy controls\nBox plot showing median, IQR and individual means") + xlab("Presence of Tone") +  ylab("Average of Shift from Baseline [ms]") + geom_point(position = position_jitter(w = 0.03, h = 0), pch=21, col="black", cex = 2, alpha = 0.8, aes(colour = Block)) + scale_fill_brewer(palette="Set1", name="Experimental Condition", breaks=c("Tone50Trials", "Tone75Trials"), labels=c("50% Tone probability", "75% Tone probability")) +  theme(axis.title = element_text(face="bold", size=12), axis.text  = element_text(face="bold", size=10), axis.ticks = element_blank()) + facet_grid(. ~ Status,labeller=CS_labeller)
```


**Potential outliers based on mean**
```{r echo= FALSE,results='asis',error=F,warning=F}
kable(Out_mean, format = "markdown")
```

####Outliers based on standard deviation of baseline corrected judgement erorrs
```{r, echo = FALSE, comment="  ",fig.width =8, fig.height=6,fig.align ='center', warning=FALSE, fig.cap='Box plot'}
  
ggplot(data=subset(dataSE3, Block != "Tone0Trials"), aes(x=TonePresence, y=sd, fill=Block)) + stat_boxplot(geom ='errorbar')+ geom_boxplot(outlier.size = 0) + ggtitle("All schizophrenia patients and healthy controls\nBox plot showing median, IQR and individual standard deviations") + xlab("Presence of Tone") +  ylab("Standard deviation of Shift from Baseline [ms]") + geom_point(position = position_jitter(w = 0.03, h = 0), pch=21, col="black", cex = 2, alpha = 0.8, aes(colour = Block)) + scale_fill_brewer(palette="Set1", name="Experimental Condition", breaks=c("Tone50Trials", "Tone75Trials"), labels=c("50% Tone probability", "75% Tone probability")) +  theme(axis.title = element_text(face="bold", size=12), axis.text  = element_text(face="bold", size=10), axis.ticks = element_blank()) + facet_grid(. ~ Status,labeller=CS_labeller)
```


**Potential outliers based on standard deviation**
```{r echo= FALSE,results='asis',error=F,warning=F}
kable(Out_sd, format = "markdown")
```

